Gradual Soundness: Lessons from Static Python

### 2022-01-26 pj-7.1/paper.tex
pj: acks, try and fail to align appendix tables

%\acks{
%  Thanks to
%  Guido van Rossum for stimulating tweets.
%  This work was partly supported by the US National Science Foundation.
%  This research was also developed with funding from the Defense Advanced Research Projects Agency (DARPA) and the Air Force Research Laboratory (AFRL).
%  The views, opinions and/or findings expressed are those of the author and should not be interpreted as representing the official views or policies of the Department of Defense or the U.S.~Government.
%  Greenman received support from NSF grant 2030859 to the CRA for the \href{https://cifellows2020.org}{CIFellows} project.
%}

@@

\begin{table}[tph]
  \caption{Richards microbenchmark data}
  \label{t:mb:richards}
  \footnotesize \centering

@@

\begin{table}[tph]
  \caption{Fannkuch microbenchmark data}
  \label{t:mb:fannkuch}
  \footnotesize\centering

@@

\begin{table}[tph]
  \caption{DeltaBlue microbenchmark data}
  \label{t:mb:deltablue}
  \footnotesize\centering

@@

\begin{tabular}{rrr}
  \colname{Orig} & \colname{Orig} & \colname{Orig} \\
  (\colname{JIT} \colname{SF}) & (\colname{JIT}) & () \\\hline
  $0.64$ & $0.78$ & $1.22$ \\
  $0.64$ & $0.81$ & $1.25$ \\
  $0.63$ & $0.81$ & $1.23$ \\
  $0.62$ & $0.79$ & $1.2$ \\
  $0.67$ & $0.81$ & $1.23$ \\
  $0.7$ & $0.8$ & $1.23$ \\
  $0.68$ & $0.78$ & $1.34$ \\
  $0.66$ & $0.79$ & $1.22$ \\
  $0.69$ & $0.85$ & $1.23$ \\
  $0.68$ & $0.79$ & $1.24$ \\
\end{tabular}

\begin{table}[tph]
  \caption{Exact commands to invoke each benchmark (1/2)}
  \label{t:mb:commands}
  \tiny\centering

@@

\begin{table}[tph]
  \caption{Exact commands to invoke each benchmark (2/2)}
  \label{t:mb:commands}
  \tiny\centering

>>>>

\acks{
  \SP{} was developed by Sinan Cepel, William Meehan, Carl Meyer, Aniket Panse,
  and Dino Viehland.
  The Brown authors contributed to the language by modeling it independently; they
  are not part of the \SP{} team.

  This work was partly supported by the US National Science Foundation.
  %% Greenman received support from NSF grant 2030859 to the CRA for the \href{https://cifellows2020.org}{CIFellows} project.
  This research was also developed with funding from the Defense Advanced Research Projects Agency (DARPA) and the Air Force Research Laboratory (AFRL).
  The views, opinions and/or findings expressed are those of the author and should not be interpreted as representing the official views or policies of the Department of Defense or the U.S.~Government.

  Special thanks to Guido van Rossum for helping the authors meet via Twitter
  and for his ongoing contributions to Python.
}

@@

\begin{table}[tp]
  \caption{Richards microbenchmark data}
  \label{t:mb:richards}
  \footnotesize \centering

@@

\begin{table}[tp]
  \caption{Fannkuch microbenchmark data}
  \label{t:mb:fannkuch}
  \footnotesize\centering

@@

\begin{table}[tp]
  \caption{DeltaBlue microbenchmark data}
  \label{t:mb:deltablue}
  \footnotesize\centering

@@

\begin{tabular}{rrr}
  \colname{Orig} & \colname{Orig} & \colname{Orig} \\
  (\colname{JIT} \colname{SF}) & (\colname{JIT}) & () \\\hline
  $0.64$ & $0.78$ & $1.22$ \\
  $0.64$ & $0.81$ & $1.25$ \\
  $0.63$ & $0.81$ & $1.23$ \\
  $0.62$ & $0.79$ & $1.2$ \\
  $0.67$ & $0.81$ & $1.23$ \\
  $0.7$ & $0.8$ & $1.23$ \\
  $0.68$ & $0.78$ & $1.34$ \\
  $0.66$ & $0.79$ & $1.22$ \\
  $0.69$ & $0.85$ & $1.23$ \\
  $0.68$ & $0.79$ & $1.24$ \\
\end{tabular}
\end{table}

\begin{table}[tp]
  \caption{Exact commands to invoke each benchmark (1/2)}
  \label{t:mb:commands}
  \tiny\centering

@@

\begin{table}[tp]
  \caption{Exact commands to invoke each benchmark (2/2)}
  \label{t:mb:commands}
  \tiny\centering
